A Particle Swarm Optimisation-Based Indirect Approach to Web Service Composition

### 2015-10-26 paper.tex
Fixed typo in one of the algorithms.

\begin{algorithm}[!htb]
\setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{filterByLayer}{filterByLayer}\SetKwFunction{mergeLayers}{mergeLayers}\SetKwFunction{findHighestTime}{findHighestTime}
 \SetKwFunction{eNull}{null}\SetKwFunction{getInputsSatisfied}{getInputsSatisfied}\SetKwFunction{calculateFitness}{calculateFitness}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{$end$, sorted layers $L$}
 \Output{fitness $f$}
 Initialise variables to keep track of QoS: $cost=0, availability=1, reliability=1$\;
 Set all inputs of $end$ as the next to satisfy, associating each input with time $0$ and layer $|L|+1$\;
 \For{all sorted layers in L, from $end$ to first}{
 	Identify the inputs from next-to-satisfy set that correspond to services in this layer\;
    \While{not all of these inputs have been satisfied}{
	Find the next service from the previous layers with the highest weight\;
	\If{service outputs satisfy at least one input}{
		Update running QoS values with service QoS (add to running cost, multiply with running availability and reliability)\;
		Add the inputs of service to the set of next inputs to satisfy, each associated with (service time + highest time from satisfied inputs) and current layer position\;
    }
 }
 Find the total composition time as the highest from the remaining set of next inputs to satisfy\;
 Calculate fitness $f$ using total QoS values\;
 \Return $f$\;
\caption{Algorithm for decoding solutions and calculating their fitness.}
\label{solutionDecoding}
\end{algorithm}

>>>>

\begin{algorithm}[!htb]
\setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{filterByLayer}{filterByLayer}\SetKwFunction{mergeLayers}{mergeLayers}\SetKwFunction{findHighestTime}{findHighestTime}
 \SetKwFunction{eNull}{null}\SetKwFunction{getInputsSatisfied}{getInputsSatisfied}\SetKwFunction{calculateFitness}{calculateFitness}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{$end$, sorted layers $L$}
 \Output{fitness $f$}
 Initialise variables to keep track of QoS: $cost=0, availability=1, reliability=1$\;
 Set all inputs of $end$ as the next to satisfy, associating each input with time $0$ and layer $|L|+1$\;
 \For{all sorted layers in L, from $end$ to first}{
 	Identify the inputs from next-to-satisfy set that correspond to services in this layer\;
    \While{not all of these inputs have been satisfied}{
	Find the next service from the previous layers with the highest weight\;
	\If{service outputs satisfy at least one input}{
		Update running QoS values with service QoS (add to running cost, multiply with running availability and reliability)\;
		Add the inputs of service to the set of next inputs to satisfy, each associated with (service time + highest time from satisfied inputs) and current layer position\;
 }}}
 Find the total composition time as the highest from the remaining set of next inputs to satisfy\;
 Calculate fitness $f$ using total QoS values\;
 \Return $f$\;
\caption{Algorithm for decoding solutions and calculating their fitness.}
\label{solutionDecoding}
\end{algorithm}
